---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# rAMPL

[![Travis build status](https://travis-ci.org/ruaridhw/r-AMPL.svg?branch=master)](https://travis-ci.org/ruaridhw/r-AMPL) [![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/ruaridhw/r-AMPL?branch=master&svg=true)](https://ci.appveyor.com/project/ruaridhw/r-AMPL)

Provides convenience wrappers around the Python package `amplpy` using `reticulate`.

## Installation

You can install AMPL from GitHub with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("ruaridhw/r-AMPL")
```

As this package relies on the `amplpy` API you will need
a Python installation and the required package.

You can check if you have Python installed by opening a Terminal
and running:

```{bash}
python -V
```

If this doesn't print a Python version, you will need to install it
first and then run:

```{bash pip-install, eval=FALSE}
pip install amplpy
```

You can obviously run this with Anaconda or a Python installation other
than the system default.

## Usage

This is a basic example which shows you how to solve a common problem.

First, start an AMPL environment. The default path is `/Applications/ampl`
and assumes you have an AMPL binary installed here.

```{r}
library(AMPL)
ampl <- ampl_env()
```

Next, we will point to the location of the model and data files.
This package includes the AMPL book's example models so we'll use its "steel"
model:

```{r}
model_file <- system.file("models/steel.mod", package = "AMPL")
data_file <- system.file("models/steel.dat", package = "AMPL")
```

Finally, run the model:

```{r example}
ampl <- set_solver(ampl, "/Applications/ampl/cplex")
ampl <- read_model(ampl, model_file)
ampl <- read_data(ampl, data_file)
ampl <- solve_model(ampl)
ampl$close()
```

Using the `magrittr` pipe to chain commands, this can be executed without
continuously repeating assignment:

```{r}
ampl <- ampl_env() %>%
  set_solver("/Applications/ampl/cplex") %>%
  read_model(model_file) %>%
  read_data(data_file) %>%
  solve_model()
steel_results <- get_data_all(ampl)
ampl$close()

steel_results$Parameters$market
steel_results$Variables
steel_results$Objectives
```
